Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-20 paper.tex
Add survival probability figures

\subsubsection*{Acknowledgements}
This research is supported in part by the Joint Institute for Nuclear
Astrophysics---Center for the Evolution of the Elements (JINA-CEE)
and the National Science Fondation under grant numbers X. \todo{grant nos?}
We thank Sherwood Richers for providing his neutrino transport code
\lstinline{Sedonu}~\footnote{\url{https://bitbucket.org/srichers/sedonu}}
for comparisons,
Fran\c{c}ois H\'{e}bert for his timely help in finding and
correcting bugs in the time-interpolation algorithm,
and Luke Roberts for helpful discussions.

>>>>

\subsubsection*{Acknowledgements}
This research is supported in part by the Joint Institute for Nuclear
Astrophysics---Center for the Evolution of the Elements (JINA-CEE)
and the National Science Fondation under grant numbers X. \todo{grant nos?}
We thank Sherwood Richers for providing his neutrino transport code
\lstinline{Sedonu}~\footnote{\url{https://bitbucket.org/srichers/sedonu}}
for comparisons.
We thank Luke Roberts and Yonglin Zhu for helpful discussions.
We are indebted to Fran\c{c}ois H\'{e}bert for his timely help in finding and
correcting bugs in the time-interpolation algorithm.
